\section{Message from the Tutorial Co-Chairs}\vspace{2em}
\setheaders%
    {Message from the Tutorial Co-Chairs}%
    {Message from the Tutorial Co-Chairs}
\thispagestyle{emptyheader}

\setlength{\parskip}{1ex}

Welcome to the Tutorials Session of NAACL HLT 2018 in New Orleans.

The NAACL-HLT tutorials session is an opportunity for conference attendees to participate in a tutorial on a timely topic of importance to the field, and to hear from experts on that topic. This year, the tutorials committee comprised of tutorials chairs from four conferences: ACL, COLING, EMNLP and NAACL-HLT. A total of 51 tutorial submissions were received, of which 6 were selected for presentation at NAACL-HLT.

We hope you find the six NAACL-HLT tutorials for this year to combine depth within each tutorial, and breadth across a set of topics that demonstrate the increasing relevance of NLP to a wide range of fields within and beyond computer science.

We would like to thank Marilyn Walker (NAACL general chair), Ying Lin (NAACL website chair), Stephanie Lukin and Margaret Mitchell (NAACL publications chairs), and Priscilla Rasmussen (local arrangement chair) for their help during the whole process. We also want to extend our sincere gratitude to the other conferences' tutorial chairs who jointly helped with reviewing for all the tutorial submissions: Yoav Artzi, Jacob Eisenstein, Pascale Fung, 
Donia Scott, Marilyn Walker, Mausam, and Lu Wang.

Enjoy the tutorials!

\vskip 0.5in
\noindent
NAACL 2018 Tutorial Co-chairs\\
\noindent
Mohit Bansal \\
\noindent
Rebecca Passonneau\\

\index{Bansal, Mohit}
\index{Passonneau, Rebecca}
