\section{Message from the Program Committee Co-Chairs}\vspace{2em}
\setheaders%
    {Message from the Program Committee Co-Chairs}%
    {Message from the Program Committee Co-Chairs}
\thispagestyle{emptyheader}
%\renewcommand{\large}{\fontsize{9}{11}\selectfont}
% that's a hack to make this part nicely fill the pages

\setlength{\parskip}{.7ex}
%\setlength{\parindent}{0pt}


We welcome you to New Orleans for the 16th Annual Conference of the North American Chapter of the Association for Computational Linguistics: Human Language Technologies (NAACL HLT 2018)! We had three primary goals for NAACL HLT 2018: construct a great program; manage the integrity and quality of the publication process; and ensure broad participation.

\noindent {\bf Construct a great program:}
NAACL HLT 2018 does have a great program, thanks to all of you! 
We will have three exciting keynotes, from Charles Yang, Kevin Knight and Dilek Hakkani-T\"ur. 
%\begin{itemize}[noitemsep,nolistsep]
%\item Charles Yang, University of Pennsylvania, title {\it Why 72?}
%\item Kevin Knight, University of Southern California / Information Sciences Institute, title {\it The Moment When the Future Fell Asleep}
%\item Dilek Hakkani-T\"ur, Google Research, title {\it TBD}
%\end{itemize}
% from start: long 665 66w, 16rwr, 383rfr, 207a (1w); short 458 18w, 17rwr, 298rfr, 125a (0w)
331 research track papers (206 long, 125 short), accepted following peer review, will be presented\footnote{We received 1122 research track submissions (664 long, 458 short). 33 were rejected without review and 84 were withdrawn by the authors either before, during or after review.}. Four of these papers have been identified as outstanding papers, and one will be named best paper. 
%We thank the award committeee: Joyce Chai, Michael Collins, Jennifer Foster, Smaranda Muresan and Joel Tetreault (chair).
%Area chairs nominated 19 papers; we selected 9 of these as outstanding paper candidates, and then a best paper award %committee consisting of five area chairs from different areas who had no conflicts-of-interest with the nominated papers selected four outstanding papers:
%\begin{itemize}[noitemsep,nolistsep]
%\item {\it Deep Contextualized Word Representations}, by Matthew Peters, Mark Neumann, Mohit Iyyer, Matt Gardner, %Christopher Clark, Kenton Lee and Luke Zettlemoyer
%\item {\it Learning to Map Context-Dependent Sentences to Executable Formal Queries}, by Alane Suhr, Srinivasan Iyer and Yoav Artzi
%\item {\it Neural Text Generation in Stories using Entity Representations as Context}, by Elizabeth Clark, Yangfeng Ji and Noah A. Smith
%\item {\it Recurrent Neural Networks as Weighted Language Recognizers}, by Yining Chen, Sorcha Gilroy, Andreas Maletti, %Jonathan May and Kevin Knight
%\end{itemize}
%One of these will be announced as best paper at the conference. 
We will also feature a ``Test of Time'' session with retrospectives (from the authors) on three influential papers from ACL venues. We thank the committees who nominated and voted on these paper awards.
%, nominated by our area chairs and voted on separately by two committees: an expert award committee consisting of all ACL and NAACL general chairs and program chairs and NAACL board members from 2013-2018 who did not have a conflict with the nominated papers, and a community award committee consisting of the 1000 authors who have published the most papers at ACL venues and who did not have a conflict with the nominated papers. The three Test of Time papers are:
%\begin{itemize}[noitemsep,nolistsep]
%\item {\it BLEU: a Method for Automatic Evaluation of Machine Translation}, by Kishore Papineni, Salim Roukos, Todd Ward and Wei-Jing Zhu
%\item {\it Discriminative Training Methods for Hidden Markov Models: Theory and Experiments with Perceptron Algorithms}, by Michael Collins
%\item {\it Thumbs up?: Sentiment Classification using Machine Learning Techniques}, by Bo Pang, Lillian Lee and Shivakumar %Vaithyanathan
%\end{itemize}


The main program at NAACL HLT 2018 also includes 16 TACL paper presentations, 20 demos, a student research workshop and an industry track. Keynotes from both the research and industry tracks are plenary. In a change from previous years of NAACL HLT, and motivated by EMNLP 2017, poster and oral presentation sessions will be held in parallel during the day. All posters are grouped thematically (including posters from the industry track and student research workshop and demos) and assigned to poster sessions so as to not be against oral presentation sessions with the same theme. 


\noindent {\bf Manage the integrity and quality of the publication process:} To manage load, we decided that each area chair should be responsible for no more than 30 submissions and that reviewers should be responsible for reviewing no more than 3 submissions. To help reviewers, we and the ACL program co-chairs constructed a more structured review form, with questions related to the new ACL guidelines on publication and reviewing, as well as to contribution types, experimental methods (thank you, Bonnie Webber!), software and handling of data. 

We recruited an excellent group of 72 area chairs; we thank them for their leadership, and for nominating and voting on outstanding papers, outstanding reviewers and test of time papers. 1372 individuals reviewed papers for the conference (as program committee members, ad hoc reviewers or secondary reviewers); all but 49 reviewers had no more than 3 submissions to review overall, and the 49 reviewers who took on a heavier load did so voluntarily. We thank all our reviewers, especially the ad-hoc reviewers who provided last minute reviews and the outstanding reviewers identified by the area chairs.

Submissions were assigned to area chairs and reviewers using a combination of area chair expertise, Toronto Paper Matching System (TPMS) scores and reviewer bids. Both long and short paper submissions received 3 reviews each. Long paper authors had an opportunity to respond to reviews. First-round accept/reject suggestions were made by area chairs working in small groups of 2-3 and discussing with the reviewers as necessary; final decisions were made by the program chairs. Where the reviews disagreed or there was considerable discussion, one area chair wrote a short meta review that was shared with the authors. 

This year, if the authors of a NAACL HLT 2018 submission and the author of a review for that submission both consented, then we will include the review in a review corpus to be released jointly with the program chairs of ACL, Iryna Gureyvich and Yusuke Miyao. We also asked authors of accepted papers to upload the source code for their papers. Both of these corpora will be released in the coming months.

The health of our field as a science is dependent on a scalable peer review process, which in turn depends on (a) conscientious effort from a broad pool of expert reviewers, and (b)  tools, processes and policies that can scaffold and enable reviewing. As a field we are at a breaking point: we are growing rapidly, with corresponding  heavy load on experienced researchers who participate in peer review; and we lack good tools to manage the process. Peer review involves several tasks that we, as NLP researchers, ought to be uniquely qualified to address, including expertise sourcing, network analysis and text mining. We have written a proposal with other members of the ACL community for concrete steps the ACL can take to improve our peer review infrastructure. We have also written a collection of ``how to'' documents that we will pass on to future conference organizers. 
% We urge the ACL and NAACL to support improvements to our peer review infrastructure. 

\noindent {\bf Ensure broad participation:} To ensure broad participation, we recruited program committee members using a similar method to that used for NAACL HLT 2016: we invited anyone who had published repeatedly in ACL sponsored venues, who had a PhD or significant experience in the field spanning more than 5 years, and whose email address was up to date in START. We thank Dragomir Radev for giving us a list of names from the ACL anthology. 

We also kept a blog where we discussed and attempted to ``demystify'' each stage of the publication process. This blog can be found at the conference website, {\small \url{http://naacl2018.org}}. We are very grateful to the researchers who wrote guest blog posts: Omer Levy, Gemma Boleda, Emily Bender, Nitin Madnani, David Chiang, Kevin Knight, Dan Bikel and Joakim Nivre. 

On our blog, we reported on the diversity of our area chair,  reviewer and author pools in terms of years of experience, affiliation type and geography, and gender. We will include these details in our report to the NAACL Executive Committee. We hope that future years' chairs will make similar reports.

The excellence of the overall NAACL HLT 2018 program is thanks to all the chairs and organizers. We especially thank the following people: Margaret Mitchell and Stephanie Lukin, the publication chairs; Jonathan May, the handbook chair; Yonatan Bisk and Wei Xu, the publicity and social media chairs; Ying Lin, the tireless website chair; and Marilyn Walker, the NAACL HLT 2018 general chair. We thank the chairs of NAACL HLT 2016 and ACL 2017 for their informative blogs, and the program chairs of NAACL HLT 2016, Owen Rambow and Ani Nenkova, for their advice. We thank the program co-chairs of ACL 2018, Iryna Gurevych and Yusuke Miyao, who have been very collaborative on matters related to reviewing. We thank Shuly Winter, who helped fix a serious START bug. We thank Julia Hockenmaier and the NAACL Executive Committee for their support.  We are grateful for the professional work of Rich Gerber and his colleagues at SoftConf (START), and  of Priscilla Rasmussen from the ACL. 

It has been an enormous privilege for us to see the scientific advances that will be presented at this conference. We would like to close with some advice for you, the conference attendees.  %It is a privilege to be able to attend and participate in the discussion. 
\begin{itemize}[noitemsep,nolistsep]
\item The presenters have made valuable contributions to our science; their oral, poster and demo presentations are worth your time and attention.
\item Talk to some people you haven't previously met. They may be your   future collaborators!
\item You can follow the conference on social media; we have a conference app and website where we will post any updates to the program, and our twitter handle is @naaclhlt. 
\item This event is run by a professional organization with a code of conduct ({\small \url{https://www.aclweb.org/adminwiki/index.php?title=Anti-Harassment_Policy}}). If you observe or are the recipient of unprofessional behavior, you may contact  any current member of the ACL or NAACL Executive Committees, the NAACL HLT general chair (Marilyn Walker), us (the program chairs), or Priscilla Rasmussen (acl@aclweb.org). We will hold your communications in strict confidence and consult you before taking any action.
\end{itemize}

We look forward to a wonderful conference! 

\vskip 0.5in
\noindent NAACL HLT 2018 Program Co-Chairs \\
{\it Heng Ji}, RPI \\
{\it Amanda Stent}, Bloomberg
\index{Ji, Heng}
\index{Stent, Amanda}
