\vspace{-4em}

\section{Message from the General Chair}%\vspace{2em}
\setheaders%
    {Message from the General Chair}%
    {Message from the General Chair}
\thispagestyle{emptyheader}


Welcome to New Orleans and to NAACL HLT 2018 – the biggest NAACL to
date.  Natural Language Processing and Computational Linguistics is
constantly growing and changing with a constant flow of new methods
and topics. Every year also sees an even more exciting and diverse
research community, with a steadily increasing number researchers,
companies both large and small, and a vibrant community of
practitioners and students who are excited at the prospect of taking
on the newest challenges of the discipline.  This year’s NAACL HLT
conference reflects what an exciting time this is for our field, and
highlights the vibrancy and vitality of our community.

I feel extremely lucky to be able to work with a fantastic program
committee, especially the two extremely dedicated, creative and
resourceful program chairs: Amanda Stent and Heng Ji. Their
innovations include a new review form, intended to elicit higher
quality reviews, the opportunity for authors to review the reviewers,
the Test-of-Time awards, and a program where poster and demo sessions
run consistently in parallel to the oral sessions, in order to allow
the conference to reflect the ever increasing diversity of research
topics and the corresponding volume of accepted papers.  I am
especially excited about the new Test-of-Time papers award session,
and hope to see this new innovation become a regular part of ACL
conferences.

We have	named the Test-of-Time award in memory of Aravind Joshi, who
left us this year, after having a huge lifetime impact on our
community. We will always remember him for his gentle conversational
style, sharp focus, interest in linguistic, computational and
mathematical properties of language, and his lifetime commitment to
mentoring women in NLP.	I feel extremely lucky to have been one	of his
Ph.D. students.

This year we also introduced an industrial track, with the aim of
featuring papers that focus on scalable, interpretable, reliable and
customer facing methods for industrial applications of Natural
Language Processing. The idea of having such a track was proposed by
Yunyao Li who strongly advocated for it: this proposal was then
discussed and approved by the NAACL board. After that, it was all go,
with an incredible amount of work to promote and organize it by the
industrial track chairs: Jennifer Chu-Carroll, Yunyao Li and Srinivas
Bangalore.

The overall program looks amazing and reflects the cooperative way
that everyone on the committee worked together. What a team! I am so
grateful for getting to be a part of this community of people, and I
really appreciate the enthusiasm and attention to detail reflected in
their hard work: Amanda Stent and Heng Ji (program chairs); Jennifer
Chu-Carroll, Yunyao Li and Srinivas Bangalore (industrial track
chairs); Ying Lin (website chair); Marie Meteer and Jason Williams
(workshop co-chairs); Mohit Bansal and Rebecca Passonneau (tutorial
co-chairs); Yang Liu, Tim Paek, and Manasi Patwardhan (demo
co-chairs); Chris Callison-Burch and Beth Hockey (Family-Friendly
Program Co-Chairs) Stephanie Lukin and Meg Mitchell (publication
co-chairs); Jonathan May (handbook chair); Silvio Ricardo Cordeiro,
Shereen Oraby, Umashanthi Pavalanathan, and Kyeongmin Rim (student
cochairs) along with Swapna Somasundaran and Sam Bowman (Faculty
Advisors) for the student research workshop; Lena Reed (student
volunteer coordinator); Kristy Hollingshead, Kristen Johnson, and
Parisa Kordjamshidi (local sponsorships and exhibits cochairs);
Yonatan Bisk and Wei Xu (publicity and social media chairs); David
Yarowsky and Joel Tetreault (treasurers) and Alexis Palmer and Jason
Baldridge (the NAACL international Sponsorship Team). Also thanks to
Rich at SoftConf for his speedy response to questions and his
willingness to help us innovate with our new review form. And thanks
to Julia Hockenmaier and the whole NAACL Executive Board for always
being willing to consult on any issue.

The program highlights three keynote speakers in the main track: Dilek
Hakkani-T\"{u}r, Kevin Knight, and Charles Yang. We also have two keynote
speakers in the industry track: Mari Ostendorf and Daniel Marcu. These
talks promising to be interesting across a range of issues from
language acquisition in children to the commercial possibilities
of conversational agents. The industry track will also feature
two panels, one on careers in industry (as compared to academia)
and the other on ethics in
NLP. The program also includes six tutorials featuring topics
of current interest and sources of innovation in the field.
We have sixteen workshops
plus the student research workshop: some of these workshops have become
events in themselves with many of them repeated each year.
We will also have plenary sessions for the outstanding paper awards and the
new Test-Of-Time papers award session. 

Any event of this scale can only happen with the the hard work of a
wonderful group of people. I especially want to thank the NAACL board
for being willing to consult on a range of different issues and
Priscilla Rasmussen for taking care of all the millions of details
that need to be looked after every single day to make sure the
logistical aspects of the conference come together.  I want to
especially thank Priscilla for her hard work and creativity organizing
our social event: we first will go to Mardi Gras World to see the
world of wonders created each year for the Mardi Gras. From there we
go to the river, to the dockside River City Plaza and River City
Ballroom for New Orleans' famous cuisine and libations and dancing to
live Zydeco, funk, soul and R\&B.

ACL has been working for several years to increase diversity at our
conferences and in our community. So, taking inspiration from ACL 17,
we aimed to make NAACL family friendly, by providing childcare at the
conference, and encouraging people to bring their families to the
social events and breakfasts. Diversity can also be a consequence of
the support for students to attend the conference that we receive from
the NSF, CRA-CCC and CRA-W: this subsidizes student travel to the student
research workshop as well as their registration and ACL
memberships. When combined with the support we are able to give to our
student volunteers, we aim to make it possible for students from all
over the world to come to the conference and be part of our
community. We also decided, in consultation with the NAACL board, to
provide subsidies to the Widening NLP workshop, which is only being
held for the second time at this year's NAACL (last year called the
Women in NLP workshop).  These subsidies enable participation from
students and young researchers from developing countries to attend the
conference.


I am grateful to our sponsors for their generous contributions, which
add so much to what we can do at the conference. Our Diamond sponsors
are Bloomberg, Google, and Toutiao AI Lab. The Platinum
sponsor is Amazon. The Gold Sponsors are Ebay, Grammarly, IBM Research, KPMG, Oracle, Poly AI,
Tulane University, Capital One and Two Sigma. The Silver sponsors are Nuance and
Facebook, and the Bronze sponsors are iMerit and USC/ISI.

Finally, there are many more people who through their hard work and
dedication have contributed to make this conference a success: the
area chairs, workshop organizers, tutorial presenters, student
mentors, and reviewers. And of course you all, the attendees without
whom there would be no conference: you are the life and spirit of the
conference and the NAACL community. I hope you all have a
fun and exciting time at NAACL HLT 2018!

\noindent NAACL HLT 2018 General Chair \\
{\it Marilyn Walker}, University of California Santa Cruz \index{Walker, Marilyn}
