\chapter{On-Site Childcare}

NAACL 2018 will be offering on-site childcare at the conference hotel by advanced reservation or walk-in.   Walk-ins are subject to availability, but there should be plenty of space, so please bring your kids!  The cost of the childcare is partially subsidized by the NAACL. The cost for general registrants will be \$80 USD per day per child. For students registrants the cost will be \$40 USD per day per child.

%The childcare rooms are located in Strand 3 and 4 which are across from the xxx. 
The care is available for children 6 months to 12 years old from 8:30 a.m. to 6 p.m. during the main conference, plus the tutorials and workshop days. The carer givers are from a professional childcare company, KiddieCorp, all of whom are CPR/first aid certified and with child care experience. The childcare has activities and play materials such as arts and crafts as well as appropriate toys for babies as well as a quiet area for napping.  

In addition to childcare, we invite you to bring your children, spouses and loved ones to the social event at the conference. You can purchase additional meals or additional tickets to the social event for your family members. The social event for this year is an evening at the Mardi Gras World museum. It's a family friendly venue, and we hope to see you and your family there!



\emph{Below is information from KiddieCorp about their services.}


Hello NAACL Parents!

Thank you very much for your interest in the NAACL's children's program.
Our goal is to provide your children with a program they want to attend,
while providing you with that critical ``peace of mind'' feeling so you can
attend the conference activities without worrying.

KiddieCorp is pleased to provide a children's program during NAACL 2018.
KiddieCorp has more than thirty years of experience providing high quality
children's programs and youth services to conventions, trade shows and
special events. We take caring for your children very seriously. KiddieCorp
has enjoyed a long-time partnership with the American Academy of Pediatrics,
which has helped to establish KiddieCorp as a premier provider of event
children's program services.  This is the second year we have provided
services for ACL conferences - we started last year at ACL 2017 in
Vancouver. 


\paragraph{Activities} Activities include exciting themes, arts  and  crafts, group games, music
and  movement, board games, story time, dramatic play, etc. We provide
activities appropriate for each age group, using safe, sturdy equipment that
you can feel comfortable with. Children can make their own choices within
KiddieCorp's program.


\paragraph{Commitment} Our goal is to provide your children with a comfortable, safe and happy
experience. Our staff to child ratios are high to ensure that every child
feels special (1:2 for children ages 6 months through 11 months old; 1:3 for
children ages 1 through 2 years old; 1:5 for children ages 3 through 5 years
old; 1:7 for children ages 6 through 12 years old). KiddieCorp team members
are selected according to their integrity, experience, education and
enthusiasm. They must be wonderful with kids! In addition to our competitive
and selective hiring process, KiddieCorp remains at the top of the industry
by carrying ample liability insurance.


\paragraph{Where, When, For Whom} The program is for children ages 6 months through 12 years old. The dates
for the program are June 1 to June 6, 2018  and will be located in the \textbf{XXX}
room in the at the Hyatt Regency New Orleans hotel.  Snacks and beverages
will be provided and meals need to be supplied by parents when checking in
your child each day.

You will also have the option to purchase lunch for your child(ern) at
registration. The cost will be around \$15 and must be ordered by 10:00am each day and
paid in cash only. 


\paragraph{Other Info}

\begin{itemize}
\item Please label your child's belongings. We will maintain a lost and found,
however, KiddieCorp does not accept responsibility for the loss or theft of
any toy, book, or other personal items.
\item For parents with infants, please bring diaper changing supplies,
formula/baby food, and a change of clothes.
\item Cancellation Policy: Cancellations must be made to KiddieCorp prior to
May 1, 2018 for a full refund. Cancellations made after that date will be
subject to a 50\% cancellation fee. Once the program has begun, no refunds
will be issued.
\item KiddieCorp staff does not administer medication. To ensure a safe and
fun-filled environment, any child who is ill will not be admitted to the
children's program.
\end{itemize}


\paragraph{Need more information?} KiddieCorp is always available to answer any questions. Feel free to
contact KiddieCorp's by phone at 858-455-1718 or by email at
Amber@KiddieCorp.com. 


\paragraph{Example activities - Space Explorer}

Children will participate in different group games, arts \& crafts, reading,
and much more! 
Five, Four, Three, Two, One, Blast off!  It’s time to go to KiddieCorp
Space Explorer Camp.  
Bounce into our space dome tents and let our creativity take off.



Let’s imagine what zero gravity feels like when we make our own
pair of moon boots out of paper bags.  The masterpieces we create 
at the art table can include play dough alien life forms, foam planet 
bracelets and paper plate spaceships.

When we get back on earth, we can rediscover gravity by tossing
the balls in the air with the parachute. We’ll also have a chance to 
play astronaut ring toss, musical planets, and moon, moon, star 
(our version of duck, duck, goose).  So let’s buckle our seat belts, 
prepare for countdown, and blast off to KiddieCorp Space Explorer Camp.
