\section{Keynote Address: Charles Yang}
\index{Yang, Charles}

\begin{center}
\begin{Large}
{\bfseries\Large Why 72?}\vspace{1em}\par
\end{Large}

\daydateyear, 9:00--10:00 \vspace{1em}\\
\PlenaryLoc \\
\vspace{1em}\par
\end{center}

\noindent
{\bfseries Biography:} Charles is a Professor of Linguistics, Computer Science, and Psychology at the University of Pennsylvania and directs the Program in Cognitive Science. He has spent a long time to work out the tricks children use to learn languages and is now ready to try them out on machines. His most recent book, The Price of Linguistic Productivity, is the winner of the 2017 LSA Leonard Bloomfield award.

\vspace{2ex}\centerline{\rule{.5\linewidth}{.5pt}}\vspace{2ex}
\setlength{\parskip}{1ex}\setlength{\parindent}{0ex}

\section{Keynote Address: Mari Ostendorf}
\index{Ostendorf, Mari}

\begin{center}
\begin{Large}
{\bfseries\Large Building a Socialbot: Lessons Learned from 10M Conversations}\vspace{1em}\par
\end{Large}

\daydateyear, 14:00--15:00 \vspace{1em}\\
\PlenaryLoc \\
\vspace{1em}\par
\end{center}

\noindent
{\bfseries Abstract:} Researchers in artificial intelligence have long been interested in the challenge of developing a system that can converse with humans, but much of the research has focused on text-based interactions and constrained contexts. This talk looks at open domain, spoken interactions enabled by a socialbot -- Sounding Board -- designed to be a conversational gateway to the web. The recent Alexa Prize competition made it possible for the Sounding Board team to develop a socialbot, learning from millions of conversations with real users. This talk will describe the system architecture and what we learned from all these interactions, emphasizing issues related to working with speech, online content and user variation that impact future directions for the field and for university-industry partnerships.

\noindent
{\bfseries Biography:} Mari is a professor of Electrical Engineering and Associate Vice Provost for Research at the University of Washington. She is a Fellow of IEEE and ISCA, and winner of the 2018 IEEE James L. Flanagan Speech and Audio Processing Award. Her recent research has emphasized social communication, and she served as a faculty advisor for the student team winning the inaugural AlexaPrize competition to build a socialbot.


\newpage
